This section does not aim to be complete.

\textbf{Authentication Engine}

Test registration and login.
Integration: test login via external login provider.

\textbf{External Login Adapter}

Test login via external login provider, both for first time user and already registered user.
Test different external login provider.

\textbf{User Controller}

Test the creation of a user and the editing of its profile (in particular change the password and the primary mail).
Test the addition/removal of a contact, the creation of a group and the signup to an existing group.
Test the addition of an auto-decline status and the refusal of all meeting invitations in its period.
Test the edit of the preference list.
Test the addition/removal/modification of a default location.

\textbf{User Search Engine}

Test searching for a user given its nickname, its email or parts of it.
Test searching for a non-existent user.

\textbf{Constraint Engine}

Test checking for constraint that holds and for constraints that does not hold.
Integration: test adding/removing a constraint for a user.

\textbf{Meeting Controller}

Test the creation of a meeting and the editing of all its fields.
Test the recreation of a meeting.
Test the invitation of user from both the contacts of an administrator of by searching them.
Test the approval/refusal/rescheduling of a meeting.
Integration: test the receipt of a meeting invitation that triggers an update of the schedule.

\textbf{Chat Engine}

Test sending messages and retrieving them, both one at a time and in bursts.
Test sending messages from different users at the same time.
Integration: test sending messages from a user who's not in the meeting.

\textbf{Late User Engine}

Test the visualization and the dispatch of messages to late users.
Integration: test accessing the dashboard with a non-administrator.

\textbf{File Uploader}

Test uploading files with different extensions and different sizes.
Test downloading them.
Test uploading malaware.

\textbf{Travel Planner}

Test planning travels between random points and check that at least one is always returned.

\textbf{Real-Time Indications Engine}

Test the activation of this component when a meeting is approaching.
Test the indications by following them and checking they are right; requires someone physically going around.

\textbf{External Shortest Path Adapter}

Test toghether with the Travel Planner.

\textbf{External Geolocalization Adapter}

Test that the position of a user is always updated and precise; requires someone physically going around.

\textbf{Meeting Scheduler}

Test inserting a meeting in an empty schedule and in one with already a lot of meetings.
Test schedule update after a warning is solved.
Test the correct visualization of a schedule.
Integration: test inserting a meeting in an empty schedule with a lot of breaks.

\textbf{Break Manager}

Test the update of a break multiple times by different meetings.

\textbf{Rescheduling Engine}

Test the creation of a new rescheduling proposal, the approval/rejection by an administrator and the polling.
Test voting on a poll and sending the last vote, that should trigger an automatic rescheduling approval/rejection.

\textbf{Notification Engine}

Test the gathering of all the notification for a user who has lots of meetings, breaks, messages not read, ....
Test the automatic push of notifications on the application client.
Integration: test the approval/refusal/rescheduling of a meeting via the Notification Engine.