\subsubsection{Definitions}

The following list contains all the main terms we will refer to in the rest of the document, together with a brief explanation of their meaning in this context.

\begin{itemize}
\item~ \textbf{Items to be added while working}: mainly we will include technical definitions this time
\end{itemize}

\subsubsection{Acronyms}

\begin{itemize}
\item~ \textbf{DD}: Design Document (the present document).
\item~ \textbf{UML}: Unified Modelling Language (a specification defining a graphical language for visualizing, specifying, constructing, and documenting the artifacts of distributed object systems).
\item~ \textbf{COTS}: Commercial Off-the-Shelf (software and services that are built and delivered usually from a third party vendor)
\item~ \textbf{MVC}: Model-View-Controller (a design pattern).
\item~ \textbf{URL}: Uniform Resource Locator (a reference to a web resource that specifies its location on a computer network and a mechanism for retrieving it).
\item~ \textbf{API}: Application Programming Interface (a set of subroutine definitions, protocols, and tools for building application software).
\item~ \textbf{UI}: User Interface (the space where interactions between humans and machines occur).
\item~ \textbf{UX}: User Experience (a person’s perceptions of system aspects such as utility, ease of use and efficiency).
\item~ \textbf{GPS}: Global Positioning System (a global navigation satellite system that provides geolocation and time information to a GPS receiver anywhere on Earth).
\end{itemize}

\subsubsection{Abbreviations}

%\begin{itemize}
%\end{itemize}
