The RASD is organized into 5 main sections:

\begin{enumerate}
\item {\textbf{\nameref{sect:introduction}}}: this section contains a compact and high level view on the problem and on the goals of the system to be implemented in order to address it; it also contains a glossary with the definitions of the main terms we will refer to in the rest of the document.
\item {\textbf{\nameref{sect:overview}}}: this section  describes the general factors that affect the product and its requirements, without stating specific requirements. Its contents are still at a high level of abstraction and should provide a background to understand more easily the following sections.
\item {\textbf{\nameref{sect:requirements}}}: this section contains all the software requirements at a level of detail sufficient to enable designers to design a system to satisfy those requirements, and testers to test that the system satisfies those requirements. Each requirement is stated in relation to goals and domain assumptions.
\item {\textbf{\nameref{sect:uml}}}: this section contains the description of some tipical scenarios of use of \projectname~, togheter with the relative use case diagrams and sequence diagrams. There are also present some other useful diagrams, in particular the class diagram modeling the domain of use of the service and some state chart diagrams.
\item {\textbf{\nameref{sect:alloy}}}: this section contains all the code of a formal representation of the system using the alloy language and the results of the analysis of requirements in such a setting.
\item {\textbf{\nameref{sect:appendix}}}: this section contains some information about the work behind the drafting of this document, such as the amount of time spent by each of the authors, the tools used to produce all the material and a revision history that keeps track of all the modifications.
\end{enumerate}