\begin{itemize}
	\item \textbf{{Meetings}}: A meeting is an event organized by a user with a title, a date and a location. The user who creates the event becomes the first administrator of the meeting and consequently can access to all the functionalities described in the next section. Who is invited to a meeting can accept, decline or reschedule the invitation. The rescheduling request consists in asking the administrators if it is possible to change the date of the meeting; this proposal might have been generate because this meeting is incompatible with the user's schedule and signaled by a warning of the system at the invitation. \\
	A meeting has a chat that can be used for organization e users' interaction. It is possible to upload files and add personal and public notes about meeting's topic and other participants.\\
	Meetings are divided in categories and subcategories to organize them. There is a special type of meeting called \textit{Instant Meeting }that is a meeting with only one participant and that does not last in time. Instant meetings have a title, a location exactly like others but they are instantaneous (such as bring children at school) and their presence is essential to organize schedules and travels during the day.
		
	\item \textbf{{Travels}}: The system manages the user's travels through scheduled appointments during the day. The system will a priori calculate the time that the user should use from the default location to the appointment and from 15 minutes beforehand will begin to trace the user's position to provide indications regarding the departure time and the road precisely. The available travel means are walking, driving (owned or shared), biking (owned or shared) or by public transportation.  The use of each of these may be restricted or completely inhibited by the user through constraints imposed during registration and subsequently modified. The system will propose to the user the best indications according to these constraints and user's preference list. The system will then recommend and give real time indications to the user about the first path in the weighted preference list, according to constraints imposed. While computing the best path, system will take into account of all user's meetings during the day and will choose the more suitable travel mean.
\end{itemize}