\begin{itemize}
	\item \textbf{{\large Guest}}: A guest is an unregistered user who can visit the system front end to learn about the opportunities offered by our service. You may choose to register by providing valid credentials or using a third-party service. Before registering to the system, and becoming a user, the customer cannot access any of the features offered by the system such as meeting attendance and user profile management
	\item \textbf{{\large User}}: The user is a guest who has completed the registration process. In order to have full access to the functions offered by the system, it must have provided at least one default location and submitted its preference list. The user has a profile that can be edited by adding a phone number or an additional email. Furthermore the system gives each user the opportunity to create a list of favorite contacts with which they can organize meetings easily. The user can be part of groups, such as colleagues working on the same project, to organize frequent meetings with the same people on the same topic. In addition, the system provides real time information about the best path to reach the next meeting and organizes user's lunch break according to the schedule of the day
	\item \textbf{{\large Administrator}}: The administrator is a user who has created a meeting after defining a title, a date, a location and the participants.  After the meeting has been created, the administrator can add or remove participants or designate other administrators. If a user responds to the participation request by proposing a rescheduling, the administrator can accept, decline or forward the reply to all members of the team; however the administrator has the authority to propose a change of date by itself. \newline
	It can upload files both before the meeting, to provide a complete program on the meeting topics to all participants, and after the meeting, to share their results with the team. These files can also be maintained and updated for subsequent meetings.  In fact, the administrator has the opportunity to re-propose a subsequent meeting with the same people, keeping the topic and files unchanged. \newline
	The system gives the administrator the power to monitor in real time whether a participant will arrive late, above a threshold of 15 minutes, thanks to the system's ability to trace the position of the participants
	\item \textbf{{\large System Manager}}: The system manager is an employee of \projectname~  who has the ability to maintain and update the system. It does not have an account that can use to interface with other users but must act on the system to add new features or improve existing one
\end{itemize}
